A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-11-24 01_Introduction.Rmd
work on introduction text

The spread of ideas in human populations over space and time is a major topic of *Cultural Evolution* research [@creanzaCulturalEvolutionaryTheory2017]. Archaeology has a special perspective to offer here: It's concerned with questions and data that can embrace continent size areas and millennia of cultural development and interaction [@garveyCurrentPotentialRoles2018]. Archaeological data is mostly comprised of the material remains of human behaviour -- so the ruins of past architecture, individual lost or discarded artefacts and all kinds of waste and trash. Similarity between these artefacts within and beyond cultural-historical contexts are traditionally explained by human interaction: We rightfully expect humans to learn production as well als building techniques and traditions  -- both functionally meaningful and seemingly pointless -- from others close to them. The relatedness of historically and spatially close material remains generally is a result of long-term social exchange [@lymanChronometersUnitsEarly2000; @lymanCultureHistoricalBiological2001; @lymanRiseFallCulture1997; @obrienEpistemologicalNatureArchaeological2002]. *Cultural Transmission Theory* is concerned with this exchange from the point of view of cultural evolution.

>>>>

The spread of ideas in human populations over space and time is a major topic of *Cultural Evolution* research [@creanzaCulturalEvolutionaryTheory2017]. Archaeology has a special perspective to offer here: It's concerned with questions that can embrace continent size areas and millennia of cultural development [@garveyCurrentPotentialRoles2018]. Archaeological data is mostly comprised of the material remains of human behaviour -- so the ruins of past architecture, individual lost or discarded artefacts and all more inconspicuous remains of human live. Similarity between artefacts within and beyond cultural-historical contexts are traditionally explained by interaction: We rightfully expect humans to learn production as well als building techniques and traditions  -- both functionally meaningful and seemingly pointless -- from others close to them. The relatedness of historically and spatially close material remains generally is a result of long-term social exchange [@lymanChronometersUnitsEarly2000; @lymanCultureHistoricalBiological2001; @lymanRiseFallCulture1997; @obrienEpistemologicalNatureArchaeological2002]. *Cultural Transmission Theory* is concerned with this exchange from the point of view of Cultural Evolution.
